Enhancing diagnostic of stochastic mortality models leveraging contrast trees. An application on Italian data

### 2022-11-27 Manuscript Contrast Trees_R1.tex
ok

\section*{Author contributions}
Authors equally contributed to this work.

\section*{Data availability}
The dataset analyzed during the current study, referred to Human Mortality Database (HMD), is available at \url{https://www.mortality.org/}

>>>>

\section*{Author contributions}
S.L., M.L. and A.N., equally contributed to this work.

\section*{Data availability}
The dataset analyzed during the current study, referred to Human Mortality Database (HMD), is available at \url{https://www.mortality.org/}.
The replication scripts, written in the R statistical programming
language (R. Core Team, 2013); \linebreak is available on the Open Science Framework (OSF) at 
\linebreak \url{https://osf.io/2drhc/?view_only=56b1a1e27238423d8294ee58ca38c4b1}
